\vspace{-2cm} Kronos \& Krios: Evidence for accretion of rocky planets in a comoving pair of sun-like stars \vspace{-0.5cm}

### 2017-06-28 paper/ms.tex
ack
vertical action refs. fixes #10

\section{Acknowledgements}
We thank Andy Casey for bringing $^{6}\elem{Li}$ into our attention.
We thank Megan Bedell, Andy Casey, Keith Hawkins, Nathan Leigh, and Josh Winn
for their valuable feedback.
The Flatiron Institute is supported by the Simons Foundation.
% Gaia
This work has made use of data from the European Space Agency (ESA) mission
{\it Gaia} (\url{http://www.cosmos.esa.int/gaia}), processed by the {\it Gaia}
Data Processing and Analysis Consortium (DPAC,
\url{http://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding for the DPAC
has been provided by national institutions, in particular the institutions
participating in the {\it Gaia} Multilateral Agreement.
% 2MASS
This publication makes use of data products from the Two Micron All Sky Survey,
which is a joint project of the University of Massachusetts and the Infrared
Processing and Analysis Center/California Institute of Technology, funded by
the National Aeronautics and Space Administration and the National Science
Foundation.
% all-WISE
This publication makes use of data products from the Wide-field Infrared Survey
Explorer, which is a joint project of the University of California, Los
Angeles, and the Jet Propulsion Laboratory/California Institute of Technology,
funded by the National Aeronautics and Space Administration.
% software
%\software{
%  %The data and code used in this project is available from
%  %\url{https://github.com/smoh/KronosKrios} under the MIT open-source
%  %software license.
%  This research utilized:
%  \texttt{Astropy} (\citealt{Astropy-Collaboration:2013}),
%  \texttt{emcee} (\citealt{2013PASP..125..306F}),
%  \texttt{IPython} (\citealt{Perez:2007}),
%  \texttt{matplotlib} (\citealt{Hunter:2007}),
%  \texttt{numpy} (\citealt{Van-der-Walt:2011}),
%  and \texttt{pandas} (\citealt{pandas}).}

@@

The surface lithium abundance is the only indicator of a
younger age.
If the two stars were only several hundred Myrs old, then they would likely
have been part of a larger comoving group of stars.
However, there is no evidence in our search\cite{2017AJ....153..257O} of
comoving pairs using \tgas\ that these stars belong to a larger group of
young stars.
Very young stars often show signs of activity such as
X-ray emission from magnetic activity, emission lines, or infrared excess due to
circumstellar disks (\todo{needs refernces}).
We have compiled GALEX, Tycho-2, 2MASS, and WISE photometry for these stars, and
found no evidence for indications of activity or infrared excess in their
spectral energy distributions (\figname~\ref{fig:sed}).
The low $v\sin(i)$ values (\tablename~\ref{tab:t1}) also argue against very
young ages that would be inferred from the surface lithium abundances.
Finally, we computed the Galactic orbit of the pair using the median of the
posterior sample over the phase space coordinates of \sunanalog, in a Milky
Way-like gravitational potential\cite{Bovy:2015} using \project{Gala}\cite{gala}.
The pair's fiducial orbit has a vertical action larger than the Sun, favoring
an older age (\figname~\ref{fig:orbit}).
%TODO:APW needs references for vertical action as age indicator
We therefore conclude that the two stars are most likely coeval, $\sim 4$~Gyr
old main sequence stars, and that their unusually high \elem{Li} abundance
requires an alternative explanation; our favored explanation being the accretion
of rocky material that has locked lithium.

>>>>

\section{Acknowledgements}
We thank Andy Casey for bringing $^{6}\elem{Li}$ into our attention.
We thank Megan Bedell and Andy Casey for valuable discussions,
and Keith Hawkins, Nathan Leigh, and Josh Winn for comments
on early version of the draft.
The Flatiron Institute is supported by the Simons Foundation.
% Gaia
This work has made use of data from the European Space Agency (ESA) mission
{\it Gaia} (\url{http://www.cosmos.esa.int/gaia}), processed by the {\it Gaia}
Data Processing and Analysis Consortium (DPAC,
\url{http://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding for the DPAC
has been provided by national institutions, in particular the institutions
participating in the {\it Gaia} Multilateral Agreement.
% 2MASS
This publication makes use of data products from the Two Micron All Sky Survey,
which is a joint project of the University of Massachusetts and the Infrared
Processing and Analysis Center/California Institute of Technology, funded by
the National Aeronautics and Space Administration and the National Science
Foundation.
% all-WISE
This publication makes use of data products from the Wide-field Infrared Survey
Explorer, which is a joint project of the University of California, Los
Angeles, and the Jet Propulsion Laboratory/California Institute of Technology,
funded by the National Aeronautics and Space Administration.
% software
%\software{
%  %The data and code used in this project is available from
%  %\url{https://github.com/smoh/KronosKrios} under the MIT open-source
%  %software license.
%  This research utilized:
%  \texttt{Astropy} (\citealt{Astropy-Collaboration:2013}),
%  \texttt{emcee} (\citealt{2013PASP..125..306F}),
%  \texttt{IPython} (\citealt{Perez:2007}),
%  \texttt{matplotlib} (\citealt{Hunter:2007}),
%  \texttt{numpy} (\citealt{Van-der-Walt:2011}),
%  and \texttt{pandas} (\citealt{pandas}).}

@@

The surface lithium abundance is the only indicator of a
younger age.
If the two stars were only several hundred Myrs old, then they would likely
have been part of a larger comoving group of stars.
However, there is no evidence in our search\cite{2017AJ....153..257O} of
comoving pairs using \tgas\ that these stars belong to a larger group of
young stars.
Very young stars often show signs of activity such as
X-ray emission from magnetic activity, emission lines, or infrared excess due to
circumstellar disks (\todo{needs refernces}).
We have compiled GALEX, Tycho-2, 2MASS, and WISE photometry for these stars, and
found no evidence for indications of activity or infrared excess in their
spectral energy distributions (\figname~\ref{fig:sed}).
The low $v\sin(i)$ values (\tablename~\ref{tab:t1}) also argue against very
young ages that would be inferred from the surface lithium abundances.
Finally, we computed the Galactic orbit of the pair using the median of the
posterior sample over the phase space coordinates of \sunanalog, in a Milky
Way-like gravitational potential\cite{Bovy:2015} using \project{Gala}\cite{gala}.
The pair's fiducial orbit has a vertical action larger than the Sun, favoring
an older age (\citealt{Wielen:1977,Aumer:2016}); see \figname~\ref{fig:orbit}.
We therefore conclude that the two stars are most likely coeval, $\sim 4$~Gyr
old main sequence stars, and that their unusually high \elem{Li} abundance
requires an alternative explanation; our favored explanation being the accretion
of rocky material that has locked lithium.
